Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
remove minimal_quadratic refs

In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
basis defined above is minimal.
\todo{What about $\frac{\alpha}{\beta} > 1$?}
\end{proof}

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
		\{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements
		$y_3, y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

@@

Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
\end{proof}

@@

Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
\end{proof}

@@

Next, note that the minimal generators of $I'$ together with the
new generators of $I$ given in (c) have independent initial terms
by construction, and therefore are minimal by Lemma
~\ref{lem:minimal_quadratic}.

Finally, to check (e), we will first show that $(\sx,J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx,J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

@@

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $in_\prec(I)$ generated by quadratics under grlex
with $x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$.
These quadratics must also determine minimal generators for $I$ by
Lemma ~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to
degree $e = 7$ with relations up to degree $2e = 14$, as desired.
We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
since $e_i = 9 > e$ for all $i \in J$.

>>>>

%In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
%~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
%basis defined above is minimal.
%\todo{What about $\frac{\alpha}{\beta} > 1$?}
\end{proof}

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
		\{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements
		$y_3, y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
	%\item[(c)] Any set of minimal generators for $I'$ together with 
		%any set of relations with leading terms as in (b) minimally 
		%generate $I$.
\end{enumerate}
\end{lem}

@@

%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
\end{proof}

@@

%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
\end{proof}

@@

%Next, note that the minimal generators of $I'$ together with the
%new generators of $I$ given in (c) have independent initial terms
%by construction, and therefore are minimal by Lemma
%~\ref{lem:minimal_quadratic}.

Finally, to check (e), we will first show that $(\sx, J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

@@

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $in_\prec(I)$ generated by quadratics under grlex
with $x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$.
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to
degree $e = 7$ with relations up to degree $2e = 14$, as desired.
We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
since $e_i = 9 > e$ for all $i \in J$.
